 

### 2021-06-22 vertical-thermal-review.Rmd
finished edits of "Review of vertical gradients" section

**The buffering patterns described above vary geographically, seasonally, and across forests types [REFS; *Defrenne et al. 2021*].**
The strength of buffering in high elevation, in some cases, decreases when (**THIS WILL NOT ALWAYS BE TRUE!--e.g., semi-arid regions where forest cover increases with elevation**) moving to open-forests, and increases with canopy density [@zellweger_seasonal_2019; @vonarxSpatiotemporalEffectsForest2012a; @juckerCanopyStructureTopography2018]. Buffering capacity is also greater in wetter than drier regions [**REF**] and increases with proximity to water, for example in riparian forests. [@davisMicroclimaticBufferingForests2019; @macekMaximumAirTemperature2019]
Seasonally, canopy buffering capacity is greater in wet than dry seasons, presumably because leaf area is greater in wet seasons [@davisMicroclimaticBufferingForests2019; @rey-sanchez_spatial_2016; @vonarxSpatiotemporalEffectsForest2012a; @fauset_differences_2018**double check these refs--at least one didn't belong**].

>>>>

**The buffering patterns described above vary geographically, seasonally, and across forests types [Figs. `r fig_NEON_vertical`, `r SIfig_NEON_all`, *Defrenne et al. 2021*].**
The strength of buffering increases with canopy density -- for example, across gradients of elevation [@zellweger_seasonal_2019; @vonarxSpatiotemporalEffectsForest2012a; @juckerCanopyStructureTopography2018], moisture [**REF**], and proximity to water, for example in riparian forests [@davisMicroclimaticBufferingForests2019; @macekMaximumAirTemperature2019]. (*Nidhi, please make sure the references are appropriate here-- I rearranged the sentence structure.*)
Seasonally, canopy buffering capacity is greater in wet than dry seasons, presumably because leaf area is greater in wet seasons [@davisMicroclimaticBufferingForests2019; @rey-sanchez_spatial_2016; @vonarxSpatiotemporalEffectsForest2012a; @fauset_differences_2018; **double check these refs--at least one didn't belong**].
